Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-27 extended_catalog/paper/extended_catalog.tex

\begin{abstract}
Spatial extension is an important characteristic for correctly
associating LAT sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources with the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT's threshold for
detecting the spatial extension of sources.  We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. We report the
detection of nine spatially extended sources in addition to the twelve
spatially extended sources reported in 2FGL.
\end{abstract}

@@

\hl{
Figure~\ref{all_sensitivity} shows the flux threshold
as a function of source extension for different background levels (1x,
10x, and 100x the nominal background), different spectral indices, and
two different energy bands (1 \gev to 100 \gev and 10 \gev to 100 \gev).  The detection
threshold is higher for sources in regions of higher background.  For a
fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev flux, the LAT's detection threshold
only weakly depends upon the spectral index.  This effect is most
pronounced when using only photons with energies above 10 \gev.  Overlaid
on Figure~\ref{all_sensitivity} are the LAT detected extended sources
that will be discussed in Sections~\ref{validate_known}
and \ref{new_ext_srcs_section}.  The extension thresholds are tabulated
in Table~\ref{all_sensitivity_table}.

@@

\hl{
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
Mosaic \rosat observations of Puppis A produced the highest
resolution X-ray image of this source
and contours corresponding to this
image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
inferred \gev size \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

@@

\hl{
\cite{hess_plane_survey} argued that HESS\,J1632$-$478
is positionally coincident with the hard X-ray source
IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
extension disfavors the association.  Further observations by
\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
and inside point-like emission coincident with the peak
H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
in archival MGPS-2 data a spatially coincident extended radio source
\citep{most_survey_galactic_plane}.  The positional match argues for a
single synchrotron processes producing X-ray and \gev and \tev radiation,
likely due to a PWNe.  The increased \gev and \tev size compared
to the X-ray size has previously been observed in several aging PWNe
including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
a different synchrotron cooling time for the electrons producing X-rays
and \tev $\gamma$-rays.
}

@@

Milagro detected a $4.2\sigma$
excess at energies $\sim 30 \tev$ from the location of
this source in the previous LAT bright $\gamma$-ray source
list. \cite{lat_bsl,milagro_bright_source_list}.  Veritas also detected
an extended source VER\,J2019+407 coincident with the SNR above 200
\gev and suggested the \tev emission could be a shock-cloud interaction
in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
\gev photons to avoid PSR\,J2021+4026, we resolve an
extended source whose inferred \gev size well matches the radio size of
$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049}
which overlays contours of $\gamma$-Cygni at 408MHz from the Canadian
Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
}

@@

2FGL reported the detection of twelve sources
previously resolved by the LAT at \gev energies. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to firmly associate the LAT source in many cases.

The 21 extended LAT sources are located close to the Galactic
plane and plotted in Figure~\ref{allsky_extended_sources}.  Most of the
extended sources are indeed expected to be of Galactic origin as the
distance of extragalactic sources (with exception of the local group
Galaxies) is typically too large to resolve them in $\gamma$-rays.

Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
of LAT detected extended sources and of all sources in 2FGL. This, and
Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
show that the LAT observes a population of hard (index $<2$)
extended sources at energies above 10 \gev which connects to \tev sources.
Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
extended sources which were first discovered in the H.E.S.S. Galactic
plane survey \citep{hess_plane_survey} and have a matching size to LAT
extended sources.  The LAT energy spectrum connects smoothly to \tev.
This is also true of HESS\,J1825$-$137 \citep{fermi_hess_j1825} and 
RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.

For the LAT extended sources also seen in the \tev energy range,
Figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
a good correlation between the size of the sources in the \gev and \tev
energy ranges. Even
so, the size of PWNe are expected to vary across the \gev and \tev energy
range and the size of HESS\,J1825$-$137 was seen by H.E.S.S. to vary
between 200 \gev and 20 \tev \citep{energy_dependent_hess_j1825}.
HESS\,J1825$-$137 is significantly larger in \gev than \tev
\citep{fermi_hess_j1825}.  It is interesting to compare the \gev and
\tev size of other PWN candidates, but definitively measuring this 
would require a more in-depth analysis of the LAT data using the same 
elliptical surface brightness model.

Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
field of view and all-sky coverage, the LAT can more easily measure
larger sources including the LMC and SMC.  On the other hand, the smaller
angular resolution of Air Cherenkov detectors allows them to measure a
population of extended sources below our sensitivity limit (currently at
about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with a
goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
our sensitivity to these smaller sources will improve by a factor greater
than the square root of the exposure.  With increased exposure, the LAT will likely begin to
resolve these smaller \tev sources.

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{ic443_plots/four_plots_ic443_color.eps}
    \else
    \plotone{ic443_plots/four_plots_ic443_bw.eps}
    \fi
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    Counts and test statistic profiles for the SNR IC443. (a) \ts
    vs. extension of the source. (b) \tsext for individual energy
    bands. (c) observed radial profile of counts in comparison to the
    expected profiles for a spatially extended source (solid and colored
    red in the online version) and for a point source (dashed and colored
    blue in the online version).  (d) smoothed count map after subtraction
    of the diffuse emission compared to the LAT PSF (inset).  Plots (a),
    (c), and (d) use only 1 \gev to 100 \gev photons.  Plots (c) and (d) use
    only photons which converted in the front part of the tracker and
    have an improved angular resolution.
    }
    \label{four_plots_ic443}
\end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
      \plotone{mc_plots/compare_disk_gauss_color.eps}
    \else
      \plotone{mc_plots/compare_disk_gauss_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
    \caption{
    A comparison of a 2D Gaussian and disk-like surface brightness profiles
    of extended sources before and after convolving with the PSF for two
    energy ranges.  The solid black line is the PSF that would be observed
    for a power-law source of spectral index 2. The dashed line
    and the dash-dot line are 
    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
    and the convolution of this profile with the LAT PSF respectively
    (colored red in the online version)
    The dash-dot-dot and the dot-dot line are the brightness profile of a uniform disk
    with $\rsixeight=0\fdg5$ and the convolution 
    of this profile with the LAT PSF respectively (colored blue in the online version).
    }\label{compare_disk_gauss}
  \end{figure}

@@

\tablecomments{
    A list of th spectral models of simulated point sources which were
    tested for extension.  For each model, the number of statistically
    independent simulations and the average value of \ts is also
    tabulated.  The models spans representative spectral parameters.
}
\end{deluxetable}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_ext_emin_1000_color.eps}
    \else
    \plotone{mc_plots/ts_ext_emin_1000_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
    \caption{
    Distribution of the test statistic \tsext of a likelihood ratio
    test when fitting the extension of a point source.  The four plots
    represent simulated point sources of different spectral indices and
    the different lines (colored in the online version) 
    represent point sources with different 100 \mev
    to 100 \gev integral fluxes.  The dashed line (colored red in online version)
    is the cumulative
    density function of Equation~\ref{ts_ext_distribution}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/index_sensitivity_color.eps}
    \else
    \plotone{mc_plots/index_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \caption{
    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
    uniform disk extended source for a two-year exposure.  All sources
    have an assumed power-law spectrum and the different colors correspond
    to different simulated spectral indices.  The solid line is the
    detection threshold using photons with energy between 100 \mev and 100
    \gev while the dashed line is the threshold using 1 \gev to 100 \gev photons.
    }\label{index_sensitivity}
  \end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/all_sensitivity_color.eps}
    \else
    \plotone{mc_plots/all_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \caption{the LAT detection threshold for four spectral indices and
    three background (1x, 10x, and 100x the Sreekumar-like isotropic
    spectrum) for a two-year exposure. The left plots are the detection
    threshold when using 1 \gev to 100 \gev photons and the right plots are
    the detection threshold when using 10 \gev 100 \gev photons.  The flux
    is integrated only in the selected energy range.  Overlaid on this
    plot are the LAT detected extended sources placed by the magnitude of
    the nearby Galactic diffuse emission and the energy range they were
    analyzed with.  The stars (colored red in the electronic version) are
    sources with a spectral index closer to 1.5, the triangles (colored
    blue) an index closer to 2, and the circles (colored green) an index
    closer to 2.5 The circle in plot (d) below the sensitivity line is
    MSH\,15$-$52 which was found by our analysis to have $\tsext=6.5$.
    }\label{all_sensitivity} 
  \end{figure}

@@

     1.5 &       x1 &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
         &      x10 &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
         &     x100 &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
       2 &       x1 &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
         &      x10 &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
         &     x100 &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
     2.5 &       x1 &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
         &      x10 &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
         &     x100 &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
       3 &       x1 &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
         &      x10 &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
         &     x100 &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\

@@

     1.5 &       x1 &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
         &      x10 &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
         &     x100 &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
       2 &       x1 &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
         &      x10 &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\

>>>>

\begin{abstract}
\hl{
Spatial extension is an important characteristic for correctly
associating LAT sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources with the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT's threshold for
detecting the spatial extension of sources.  We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. We report the
detection of nine spatially extended sources in addition to the twelve
spatially extended sources reported in 2FGL.
}
\end{abstract}

@@

\hl{
Figure~\ref{all_sensitivity} shows the flux threshold
as a function of source extension for different background levels 
($1\times$,
$10\times$, 
and $100\times$ the nominal background), different spectral indices, and
two different energy bands (1 \gev to 100 \gev and 10 \gev to 100 \gev).  The detection
threshold is higher for sources in regions of higher background.  For a
fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev flux, the LAT's detection threshold
only weakly depends upon the spectral index.  This effect is most
pronounced when using only photons with energies above 10 \gev.  Overlaid
on Figure~\ref{all_sensitivity} are the LAT detected extended sources
that will be discussed in Sections~\ref{validate_known}
and \ref{new_ext_srcs_section}.  The extension thresholds are tabulated
in Table~\ref{all_sensitivity_table}.

@@

\hl{
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
Mosaic \rosat observations of Puppis A produced the highest
resolution X-ray image of this source
and contours corresponding to this
image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
inferred size at \gev energies \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

@@

\hl{
\cite{hess_plane_survey} argued that HESS\,J1632$-$478
is positionally coincident with the hard X-ray source
IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
extension disfavors the association.  Further observations by
\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
and inside point-like emission coincident with the peak
H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
in archival MGPS-2 data a spatially coincident extended radio source
\citep{most_survey_galactic_plane}.  The positional match argues for a
single synchrotron processes producing X-ray and \gev and \tev radiation,
likely due to a PWNe.  The increased size at \tev energies
compared
to X-ray energies has previously been observed in several aging PWNe
including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
a different synchrotron cooling time for the electrons producing X-rays
and \tev $\gamma$-rays.
}

@@

Milagro detected a $4.2\sigma$ excess at energies $\sim 30 \tev$ from the
location of this source in the previous LAT bright $\gamma$-ray source
list. \cite{lat_bsl,milagro_bright_source_list}.  Veritas also detected
an extended source VER\,J2019+407 coincident with the SNR above 200 \gev
and suggested the \tev emission could be a shock-cloud interaction in
$\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
\gev photons to avoid PSR\,J2021+4026, we resolve an extended source
whose inferred size at \gev energies well matches the radio size of
$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049} which
overlays contours of $\gamma$-Cygni at 408MHz from the Canadian Galactic
Plane Survey \citep{canadian_galactic_plane_survey}.
}

@@

\hl{
Twelve extended sources were included in 2FGL.  Using two years of
LAT data and a new analysis method, we presented the detection of
nine additional extended sources. We also reanalyze the spatial
shape of the twelve extended sources in 2FGL.  The 21 extended
LAT sources are located close to the Galactic plane and plotted in
Figure~\ref{allsky_extended_sources}.  Most of the extended sources are
indeed expected to be of Galactic origin as the distance of extragalactic
sources (with the exception of the local group Galaxies) is typically too
large to resolve them in $\gamma$-rays.

For the LAT extended sources also seen in the \tev energy range,
Figure~\ref{gev_vs_tev_plot} shows that their is a good correlation
between the size of the sources in the \gev and \tev energy ranges. Even
so, the size of PWNe are expected to vary across the \gev and \tev
energy range and the size of HESS\,J1825$-$137 is significantly larger at
\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting to
compare the size at \gev and \tev energies
of other PWN candidates, but definitively
measuring this would require a more in-depth analysis of the LAT data
using the same elliptical surface brightness model.

Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
LAT sources to the 42 extended H.E.S.S. sources.\footnote{The 
\tev extension of
the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
Catalog. The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
Because of the large
field of view and all-sky coverage, the LAT can more easily measure
larger sources including the LMC and SMC.  On the other hand, the smaller
angular resolution of Air Cherenkov detectors allows them to measure a
population of extended sources below our sensitivity limit (currently at
about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with
a goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
the LAT's low background at high energies will allow it's sensitivity to
these smaller sources to improve by a factor greater than the square root
of the exposure.  With increased exposure, the LAT will likely begin to
detect and resolve many smaller \tev sources.

Figure~\ref{compare_index_2FGL} compares the spectral index
of LAT detected extended sources and of all sources in 2FGL. This,
and Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
show that the LAT observes a population of hard extended sources at
energies above 10 \gev.  Figure~\ref{hess_seds} shows that the
\gev spectral of
four of these sources (2FGL\,J1615.0$-$5051, 2FGL\,J1615.2$-$5138,
2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)  
connect smoothly to their \tev counterparts. This is also true of Vela
Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, RX\,J1713.7$-$3946
\citep{rx_j1713_lat}.  It is likely that the \gev and \tev emission
from these sources originates from the same population of high-energy
particles.

Many of the \tev detected extended sources now seen at \gev energies are
currently unidentified and further multi-wavelength follow-up observations
will be necessary to understand these particle accelerators. But \gev
observations of these \tev sources in many cases can help to constrain
handronic and leptonic models of these sources and, especially if their
spectra can be extended to lower energies, help to understand the emission
mechanisms producing these high energy $\gamma$-rays.  
}

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{ic443_plots/four_plots_ic443_color.eps}
    \else
    \plotone{ic443_plots/four_plots_ic443_bw.eps}
    \fi
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    Counts maps and test statistic profiles for the SNR IC443. (a) \ts
    vs. extension of the source. (b) \tsext for individual energy
    bands. (c) observed radial profile of counts in comparison to the
    expected profiles for a spatially extended source (solid and colored
    red in the online version) and for a point source (dashed and colored
    blue in the online version).  (d) smoothed count map after subtraction
    of the diffuse emission compared to the smoothed
    LAT PSF (inset).  Plots (a),
    (c), and (d) use only 1 \gev to 100 \gev photons.  Plots (c) and (d) use
    only photons which converted in the front part of the tracker and
    have an improved angular resolution.
    }
    \label{four_plots_ic443}
\end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
      \plotone{mc_plots/compare_disk_gauss_color.eps}
    \else
      \plotone{mc_plots/compare_disk_gauss_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
    \caption{
    A comparison of a 2D Gaussian and disk-like surface brightness profiles
    of extended sources before and after convolving with the PSF for two
    energy ranges.  The solid black line is the PSF that would be observed
    for a power-law source of spectral index 2. The dashed line
    and the dash-dotted line are 
    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
    and the convolution of this profile with the LAT PSF respectively
    (colored red in the online version).
    The dash-dot-doted and the dot-doted line are the brightness profile
    of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
    of this profile with the LAT PSF respectively (colored blue in the online version).
    }\label{compare_disk_gauss}
  \end{figure}

@@

\tablecomments{
    A list of the spectral models of the simulated point sources
    which were tested for extension.  For each model, the number of
    statistically independent simulations and the average value of \ts is
    also tabulated.  The models spans representative spectral parameters.
}
\end{deluxetable}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_ext_emin_1000_color.eps}
    \else
    \plotone{mc_plots/ts_ext_emin_1000_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
    \caption{
    Distribution of the test statistic for the extension test.
    The four plots
    represent simulated point sources of different spectral indices and
    the different lines (colored in the online version) 
    represent point sources with different 100 \mev
    to 100 \gev integral fluxes.  The dashed line (colored red)
    is the cumulative
    density function of Equation~\ref{ts_ext_distribution}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/index_sensitivity_color.eps}
    \else
    \plotone{mc_plots/index_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \caption{
    The detection threshold to resolve a
    uniform disk extended source for a two-year exposure.  All sources
    have an assumed power-law spectrum and the different colors correspond
    to different simulated spectral indices.  The solid line is the
    detection threshold using photons with energies between 100 \mev and 100
    \gev while the dashed line is the threshold using 1 \gev to 100 \gev photons.
    }\label{index_sensitivity}
  \end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/all_sensitivity_color.eps}
    \else
    \plotone{mc_plots/all_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \caption{the LAT detection threshold for four spectral indices
    and three background ($1\times$, $10\times$, and $100\times$ the
    Sreekumar-like isotropic spectrum) for a two-year exposure. The
    left plots are the detection threshold when using 1 \gev to 100 \gev
    photons and the right plots are the detection threshold when using
    10 \gev to 100 \gev photons.  The flux is integrated only in the
    selected energy range.  Overlaid on this plot are the LAT detected
    extended sources placed by the magnitude of the nearby Galactic
    diffuse emission and the energy range they were analyzed with.
    The star shaped markers (colored red in the electronic version)
    are sources with a spectral index closer to 1.5, the triangular
    markers (colored blue) an index closer to 2, and the circular markers
    (colored green) an index closer to 2.5.  The circular marker in plot
    (d) below the sensitivity line is MSH\,15$-$52.
    }\label{all_sensitivity} 
  \end{figure}

@@

     1.5 &      $1\times$ &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
         &     $10\times$ &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
         &    $100\times$ &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
       2 &      $1\times$ &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
         &     $10\times$ &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
         &    $100\times$ &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
     2.5 &      $1\times$ &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
         &     $10\times$ &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
         &    $100\times$ &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
       3 &      $1\times$ &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
         &     $10\times$ &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
         &    $100\times$ &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\

@@

     1.5 &      $1\times$ &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
         &     $10\times$ &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
         &    $100\times$ &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
       2 &      $1\times$ &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
         &     $10\times$ &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
         &    $100\times$ &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
